Figure 2. Bacterial Communities and Function

### 2022-02-10 reports/rmarkdown/manuscript/Figure2.Rmd

---
title: "Figure 2. Bacterial Communities and Function"
output: 
  pdf_document:
    fig_caption: yes
    keep_tex: yes
header-includes: 
- \usepackage{float}
editor_options: 
  chunk_output_type: console
---

@@

```{r Figure 2.,echo=FALSE, message=FALSE, warning=FALSE, fig.height=8}

>>>>

---
title: "Figure 2. Bacterial Communities and Function"
output: 
  pdf_document:
    fig_caption: yes
header-includes: 
- \usepackage{float}
editor_options: 
  chunk_output_type: console
---

```{r setup}
knitr::opts_chunk$set(
  fig.path="./Figures/",
  fig.process = function(filename){
    new_filename <- stringr::str_remove(string = filename, 
                                        pattern = "-1")
    fs::file_move(path = filename, new_path = new_filename)
    ifelse(fs::file_exists(new_filename), new_filename, filename)
})
#setwd("/Users/vilkal/work/Brolidens_work/Projects/Gabriella_repo/reports/rmarkdown/manuscript")
```

@@

```{r Figure 2,echo=FALSE, message=FALSE, warning=FALSE, fig.height=8}
